Decentralized Data Marketplace to Enable Trusted Machine Economy

### 2019-12-01 paper.tex
Add smart contract in Results.

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, calc, indentfirst, fancyhdr, graphicx, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, amsthm, hyphenat, natbib, hyperref, footmisc, geometry, caption, url, mdframed, tabto, soul, multirow, microtype, tikz

@@

>>>>

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, calc, indentfirst, fancyhdr, graphicx, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, amsthm, hyphenat, natbib, hyperref, footmisc, geometry, caption, url, mdframed, tabto, soul, multirow, microtype, tikz
\usepackage{listings}

@@

\subsection{Smart Contract}

In this experiment, we investigate the cost in smart contracts. We implement the smart contract and measure Gas usage. There are transaction cost and execution cost associated for an Ethereum transaction. We focus on execution cost which is included in transaction cost.

\lstdefinestyle{solidity}{
	captionpos=b,
	tabsize=4
}
\lstset{style=solidity}

\begin{lstlisting}[caption={generate contract}, label={lst:constructor}, frame=single]
	constructor(
		address _provider,
		uint _price,
		uint _brokerage,
		uint _threshold,
		string memory _channelRoot,
		string memory _endPoint,
		uint256 _totalNumber
	) public {
		broker = msg.sender;
		provider = _provider;
		isBrokerWithdraw = false;
		isProviderWithdraw = false;
		price = _price;
		totalAmount = 0;
		brokerage = _brokerage;
		threshold = _threshold;
		channelRoot = _channelRoot;
		endPoint = _endPoint;
		totalNumber = _totalNumber;
		uploadedNumber = 0;
		state = State.Launched;
	}
\end{lstlisting}

To create a Product Contract, the broker publishs the address of the data provider, subscription fee, brokerage fee, threshold of consent votes of refunding, the channel root and endpoint of MAM channel, and expected number of streaming data.

\begin{lstlisting}[caption={update blinded key and update signature}, label={lst:key_certification}, frame=single]
	function addBlindedKey(
		string memory _blindedKey
	) public {
		require(
			msg.sender == provider,
			"Only provider can add blindedKey."
		);
		require(
			state == State.Launched,
			"One key has been certified."
		);
		blindedKey = _blindedKey;
		emit newBlindedKey(blindedKey);
	}

	function addSignedBlindedKey(
		string memory _signedBlindedKey
	) public {
		require(
			msg.sender == broker,
			"Only broker can add signedBlindedKey."
		);
		require(
			state == State.Launched,
			"One key has been certified."
		);
		signedBlindedKey = _signedBlindedKey;
		state = State.KeyCertified;
		emit newSignedBlindedKey(signedBlindedKey);
	}
\end{lstlisting}

Before a data provider asks a broker to certify a session key, he blinds the session key first. The blinded session key is published to the smart contract by calling $addBlindedKey()$. The blind signature of the broker is also recorded on the smart contract. The broker should use $addSignedBlindedKey()$ to publish the signature. As a result, the key certification process is traceable afterward. It is hard for an attacker to compute the plaintext of the session key by messages on smart contracts.

\begin{lstlisting}[caption={update encrypt key}, label={lst:key_exchange}, frame=single]
	function addEncryptKey(
		address _consumer,
		string memory _encryptKey
	) public {
		require(
			msg.sender == provider,
			"Only provider can add blindedKey."
		);
		require(
			consumer2Purchase[_consumer].isKeyAdded == false,
			"One encryptKey has been added."
		);
		consumer2Purchase[_consumer].encryptKey = _encryptKey;
		consumer2Purchase[_consumer].isKeyAdded = true;
		emit newEncryptKey(_consumer, _encryptKey);
	}
\end{lstlisting}

The data provider encrypts the session key and broker's signature with the consumer's public key and call $addEncryptKey()$ to publish the ciphertext to the smart contract. Consumers listen to $newEncryptKey$ event and decrypt the ciphertext to obtain the session key.

\begin{table}[]
	\caption{Gas consumption for each function of Product Contract}
	\label{tab:gas}
	\begin{tabular}{|l|l|l|l|}
		\hline
		function & sender & transaction cost (gas) & execution cost (gas) \\ \hline
		generate contract & Broker & 2954334 & 2251002 \\ \hline
		subscribe product & Consumer & 65758 & 44486 \\ \hline
		update blinded key & Provider & 180801 & 147369 \\ \hline
		update signature & Broker & 201110 & 167678 \\ \hline
		update encrypt key & Provider & 201624 & 166784 \\ \hline
		update number & Broker & 54289 & 32825 \\ \hline
		ask refund & Consumer & 43817 & 22545 \\ \hline
		withdraw & Broker/Provider/Consumer & 35991 & 14719 \\ \hline
	\end{tabular}
\end{table}

Table \ref{tab:gas} shows the gas usage for each function. Creating a smart contract (Listing \ref{lst:constructor} ) costs the most gas, and functions (Listing \ref{lst:key_certification} and Listing \ref{lst:key_exchange} ) that are related to key certification and key exchange need a lot of gas as well. Storage on blockchain costs a lot. It is expensive to use memory in Solidity. For instance, an SSTORE operation may cost 20000 gas when the value is set to non-zero from zero\cite{Ethereum} according to Ethereum Yellow Paper. Smart contract initialization, storing ciphertexts and signatures during key certification and key exchange needs a lot of operations and storages which causes high gas consumption.
